Finding Subgraphs With Side Constraints\thanks{This research was supported by the Engineering and Physical Sciences Research Council [grant number EP/P026842/1]}

### 2021-01-25 paper/paper.tex
Add implementation section

For now we will assume that there is some way of setting up the subgraph solver and a CP solver such
that they both have this same set of variables and values, and that there is some way of knowing how
to form a correspondence between their internal representations. We will allow the CP solver to have
additional variables that the subgraph solver does not know about, and we do not specifically
require the CP solver to be aware of all of the graph constraints. We could therefore use a CP
solver as a \emph{solution checker}. Whenever the subgraph solver finds a solution, it will pass it
to the CP solver, which will treat the solution as a set of equality constraints. The CP solver will
then attempt to find a satisfying assignment. If the CP solver does not have any additional
variables, this is equivalent to simply checking that the remaining constraints hold, but otherwise
it can involve search. For a decision problem, the CP solver then communicates back to the subgraph
solver either ``yes, this is a valid solution'', or ``no, reject this solution and keep going''. If
we are solving a counting or enumeration problem, the CP solver must find \emph{all} solutions and
communicate this back to the subgraph solver.

@@

To enable communication between the two solvers, we use FIFOs (named pipes), and a simple text-based
protocol.  Both solvers are run and initialised, and then the subgraph solver proceeds as normal,
whilst the CP solver waits to be given commands. The subgraph solver thens communicate its trail
or a candidate solution as a set of assignment constraints, which the CP solver reads. The CP solver
clones its initial model, adds in the given set of constraints, and then either propagates or
searches as directed. It then communicates its success or failure state, and any deletions, back to
the subgraph solver. This approach is reasonably solver-agnostic, and adding support for different
CP solvers (or non-CP solvers) should not be difficult.

?? How does the Essence / Conjure side work?

>>>>

For now we will assume that there is some way of setting up the subgraph solver and a CP solver such
that they both have this same set of variables and values, and that there is some way of knowing how
to form a correspondence between their internal representations. We will allow the CP solver to have
additional variables that the subgraph solver does not know about, and we do not specifically
require the CP solver to be aware of all of the graph constraints. We could therefore use a CP
solver as a \emph{solution checker}. Whenever the subgraph solver finds a solution, it will pass it
to the CP solver, which will treat the solution as a set of equality constraints. The CP solver will
then attempt to find a satisfying assignment. If the CP solver does not have any additional
variables, this is equivalent to simply checking that the remaining constraints hold, but in general
this will require search.
For a decision problem, the CP solver then communicates back to the subgraph
solver either ``yes, this is a valid solution'', or ``no, reject this solution and keep going''. If
we are solving a counting or enumeration problem, the CP solver must find \emph{all} solutions and
communicate this back to the subgraph solver.

@@

Problems are specified in Essence and then are converted to concrete models that can be solved by
a CP solver (in our experiments Minion) using Conjure and Savile Row.
Running Conjure with a special flag (--graph-solver) instructs it to generate an extra file which
describes how the variables representing the graph is represented in the SavileRow input (known
as Essence'). This is used
by the graph solver so it can map between its internal state and the variables in Essence'.
SavileRow converts the graph model to Minion input, and this conversion contains information which
allows Minion to map its internal state back to the Essence' given to SavileRow. The graph solver
and Minion then communicate mappings between the nodes and edges in the graph using the
identifiers in the Essence' representation of the problem.

To enable communication between the two solvers, we use FIFOs (named pipes), and a simple text-based
protocol.  Both solvers are run and initialised, and then the subgraph solver proceeds as normal,
whilst the CP solver waits to be given commands. The subgraph solver then communicates its trail
or a candidate solution as a set of assignment constraints to the CP solver. The CP solver
then sets these assignments its state and then either performs a single propagation, or
complete search, as directed. When finished the solver communicates its success or failure state,
and any deletions (if requested), back to the subgraph solver and reverts any changes made by
setting the assignments. This approach is designed to be
solver-agnostic, and adding support for different CP solvers (or non-CP solvers) is simple, as long
as they support performing a search or propagation from a given set of assignments.
